Python and R set-up and Installations on New Computer

### 2019-12-22 nontex/install/linux/fn_ubuntu.Rmd
edit improve linux and windows installation files.

```{bash}
# could be saved in current folder: pwd
# could be saved in download folder: ~/Downloads
wget https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh
# install file
bash "Anaconda3-2019.10-Linux-x86_64.sh"
# refresh
source ~/.bashrc
```

>>>>

```{bash}
# could be saved in current folder: pwd
# could be saved in download folder: ~/Downloads
wget https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh
# install file
bash "Anaconda3-2019.10-Linux-x86_64.sh"
# refresh
source ~/.bashrc
# show all installed packages under current envir
conda list
# see where key files are installed
which python
which conda
# use conda-forge as main channel and update all
conda config --add channels conda-forge
conda update --all
```

## Install PyCharm

PyCharm can be installed from Ubuntu apps.

```{bash}
<!-- for Debian -->
sudo tar xfz pycharm-*.tar.gz -C /opt/
cd /opt/pycharm-*/bin
./pycharm.sh
```

# R install

R could be installed first as below. Or follow the [instructions on this page](https://fanwangecon.github.io/Tex4Econ/nontex/install/windows/fn_installations.html) to install from conda an environment for R, with associated R-studio.

```{bash}
apt-get update
apt-get install r-base r-base-dev
```

### 2019-12-22 nontex/install/windows/fn_installations.Rmd
edit improve linux and windows installation files.

```{bash}
# # if there are bugs
# conda clean --packages
# normal update
conda update --all
```

@@

```{r}
python "C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"
python "C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"
```

@@

1. [download R](https://cran.r-project.org/bin/windows/base/)
2. [download R-studio](https://cran.r-project.org/bin/windows/base/)
3. Open R-studio and auto-detect R
4. Install packages

```{r}
# Install R-tools
install.packages("installr")
library("installr")
install.Rtools()

@@

This did not work, *tidymodels* failed to install. Perhaps because of directory issues. *tidymodels* required *rstanarm*, and *rstanarm* failed to install.

@@

@@

```{r}
install.packages("installr")
library("installr")
# Note that this will generate several pop-up windows
install.Rtools()
# choose to only install 64 bit toolchain
# this installs g++ which is needed for rstanarm
# Add these below to windows path
# c:/Rtools/bin;
# c:/Rtools/mingw_62/bin;

>>>>

```{bash}
# # if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --add channels conda-forge
# normal update
conda update --all
```

@@

```{r}
# windows
python "C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"
python "C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"
# linux
python ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py
python ~/PyFan/ProjectSupport/graph/subplot.py
```

@@

1. [download R](https://cloud.r-project.org/)
2. [download R-studio](https://rstudio.com/products/rstudio/download/)
3. Open R-studio and auto-detect R
4. Install packages

note that installation will not work if the machine's version of R is not up to date, this could be the case with default R versions for some linux installations.

```{r}
# Install R-tools
install.packages("installr")
library("installr")
install.Rtools()
# c:/Rtools/bin;
# c:/Rtools/mingw_32/bin;
# c:/Rtools/mingw_64/bin;

@@

This did not work in windows, *tidymodels* failed to install. Perhaps because of directory issues. *tidymodels* required *rstanarm*, and *rstanarm* failed to install.

@@

For linux, note that rstudio offers Ubuntu as well as Debian versions that can be installed with wget:

```{bash}
<!-- for ubuntu -->
wget "https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"
sudo apt install ./rstudio-1.2.5033-amd64.deb
<!-- for debian -->
wget "https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"
sudo apt install ./rstudio-1.2.5033-amd64.deb
conda install -c r rstudio
cd "C:/Program Files/RStudio/bin"
rstudio.exe

@@

```{r}
install.packages("installr")
library("installr")
# Note that this will generate several pop-up windows
install.Rtools()
# choose to only install 64 bit toolchain
# this installs g++ which is needed for rstanarm
# Add these below to windows path
# c:/Rtools/bin;
# c:/Rtools/mingw_64/bin;
